---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
set.seed(2350)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


# woods

Experimental R package for double random forests


## Installation

To install the development version from GitHub, type the following commands within the R session:

```{r gh-installation, eval = FALSE}
install.packages("devtools")
devtools::install_github("beerda/woods")
```


## Usage

Firstly, load the package to start using the `woods` library:
```{r}
library(woods)
```

Then create some input data:

```{r}
d <- data.frame(y = 1:5, a = 2 * (1:5), b = 3 * (1:5))
print(d)
```

To train the `woods` model with columns `a`, `b` being the independent variables and `y` being the target, the following command has to be executed:

```{r}
fit <- woods(y ~ a + b, data = d)
print(fit)
```

Analogously we run the algorithm e.g. on iris dataset:

```{r}
fit <- woods(Species ~ Sepal.Length + Sepal.Width, data = iris, node_size = 5)
print(fit)
```

The fitted woods model may be used to classify the new data as follows:

```{r}
predict(fit, iris)
```
