---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
set.seed(2350)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


# woods

Experimental R package for double random forests


##  Implemented Features

- creation of a binary decision tree based on data
- both numerical and categorical inputs are allowed (categorical inputs are transformed to sets of dummy 0/1 variables)
- numerical target allowed:
  - node splitting by the Sum of Squared Error (SSE)
  - leaf node -- average value
- categorical target allowed:
  - node splitting by the Information Gain Ratio (IGR)
  - leaf node -- mode (the most frequent value)
- bootstrapping available to create sets of trees (a forest)


## Installation

To install the development version from GitHub, type the following commands within the R session:

```{r gh-installation, eval = FALSE}
install.packages("devtools")
devtools::install_github("beerda/woods")
```


## Usage

Firstly, load the package to start using the `woods` library:
```{r}
library(woods)
```

Then create some input data:

```{r}
d <- data.frame(y = 1:5, a = 2 * (1:5), b = 3 * (1:5))
print(d)
```

To train the `woods` model with columns `a`, `b` being the independent variables and `y` being the target, the following command has to be executed:

```{r}
fit <- woods(y ~ a + b, data = d)
print(fit)
```

Analogously we run the algorithm e.g. on iris dataset:

```{r}
fit <- woods(Species ~ Sepal.Length + Sepal.Width, data = iris, node_size = 5)
print(fit)
```

The fitted woods model may be used to classify the new data as follows:

```{r}
predict(fit, iris)
```


## Fuzzy Transform

- a kernel-based approximation of function `f` (from discrete values)
- domains have to be bounded
- input domains are partitioned by fuzzy sets
- each fuzzy set of the partition is assigned with:
  - 0-order f-transform: an average value of the original function `f`
  - 1-order f-transform: a linear function fitted to the values of `f`
  - n-order f-transform: a polynomial function fitted to the values of `f`
- fitting is based on weighting by the membership degrees of inputs to the fuzzy sets of the partitions

```
y ^
  |                             _____
  |           __*____         */    *\
  |          /       \_       /       \
  |       * /         *\__*__/         \*
  |      __/                            \
  |   __/
  |  /*
  | /
  |/
  +------------------------------------------>
                                             x
      _    _    _    _    _    _    _    _  
     / \  / \  / \  / \  / \  / \  / \  / \  
    /   \/   \/   \/   \/   \/   \/   \/   \  
   /    /\   /\   /\   /\   /\   /\   /\    \  
 ```
 
